Pillar 1 - Sequential Pattern Mining

### 2019-01-28 Pillar 1 - Sequential Pattern Mining.Rmd
debugging AR

d_transactions <- d_course %>%

  # Exclude 
  filter(
    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad
    ) %>%

@@

  # Create transactions (student level)
transactions_PF <- d_transactions_PF %>%
  group_by(`Student ID`) %>%
    summarize(list_course = list(`Course ID`)) %>%
  ungroup

@@

## Apriori Algorithm
We apply Apriori algorithm:
```{r AR apriori}

# TODO: conmpute support RHS

AR <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0, # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = NULL,
  control = list(
    verbose = FALSE
  )
  ) %>%
  inspect

colnames(AR)[2] <- "=>"
```

@@

# Apply apriori
AR_PF <- apriori(
  data = transactions_PF, 
  parameter = list(
    supp = 0, # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = list(
    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
    ),
  control = list(
    verbose = FALSE
    )
  ) %>%
  inspect

colnames(AR_PF)[2] <- "=>"
```

>>>>

```{r}
d_transactions <- d_course %>%

  # Exclude 
  filter(
    Type != "Mandatory",                  # (i) mandatory courses e.g. COR, CAP, etc
    ! Letters %in% c("SKI", "PRO",        # (ii) skills & projects (taken by majority of students)
                     "SAS", "SAH", "SAC") # (iii) courses of semester abroad (uninformative)
    ) %>%

@@

  # Create transactions with pass/fail
transactions_PF <- d_transactions_PF %>%
  group_by(`Student ID`) %>%
    summarize(list_course = list(`Course ID`)) %>%
  ungroup

@@

## Apriori Algorithm
```{r}
clean_AR <- function(AR){

  AR %>%
    as("data.frame") %>%
    filter(
      count >= 1
    ) %>%
    mutate(
      rules = str_remove(rules, pattern = "_fail"),
      lhs = substr(rules, 2, 8),
      rhs = substr(rules, 15, 21),
      `rhs.support` = confidence / lift
      ) %>%
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
      ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
      ) %>%
    arrange(
      desc(count)
    )

}
```

We apply Apriori algorithm:
```{r AR apriori}
AR <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0,    # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = NULL,
  control = list(
    verbose = FALSE
    )
  ) %>%
  clean_AR

@@

# Apply apriori
AR_PF <- apriori(
  data = transactions_PF, 
  parameter = list(
    supp = 0, # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = list(
    both = course_id_fail$`Course ID` # only include rules with fail on LHS and RHS
    ),
  control = list(
    verbose = FALSE
    )
  ) %>%
  clean_AR
```
